\documentclass[11pt]{article} 
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{graphicx}
%\usepackage[siunitx]{circuitikz}
\usepackage{tikz}
\usepackage[colorinlistoftodos, color=orange!50]{todonotes}
\usepackage{hyperref}
\usepackage[numbers, square]{natbib}
\usepackage{fancybox}
\usepackage{epsfig}
\usepackage{soul}
\usepackage[framemethod=tikz]{mdframed}
\usepackage[shortlabels]{enumitem}
\usepackage[version=4]{mhchem}
\usepackage{multicol}

\usepackage{mathtools}
\usepackage{comment}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{listings}
\usepackage{color}
\usepackage[numbers]{natbib}
\usepackage{subfiles}
%\usepackage{tkz-berge}


\newtheorem{prop}{Proposition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{cor}{Corollary}[prop]

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{definition}
\newtheorem{required}{Problem}

\theoremstyle{definition}
\newtheorem{ex}{Example}


\setlength{\marginparwidth}{3.4cm}
%#########################################################

%To use symbols for footnotes
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
%To change footnotes back to numbers uncomment the following line
%\renewcommand*{\thefootnote}{\arabic{footnote}}

% Enable this command to adjust line spacing for inline math equations.
% \everymath{\displaystyle}

% _______ _____ _______ _      ______ 
%|__   __|_   _|__   __| |    |  ____|
%   | |    | |    | |  | |    | |__   
%   | |    | |    | |  | |    |  __|  
%   | |   _| |_   | |  | |____| |____ 
%   |_|  |_____|  |_|  |______|______|
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{
\normalfont \normalsize 
\textsc{CSCI 3104 Fall 2021 \\ 
Instructor: Profs. Grochow and Waggoner} \\
[10pt] 
\rule{\linewidth}{0.5pt} \\[6pt] 
\huge Requizzing Period 1- Standard 5 \\
\rule{\linewidth}{2pt}  \\[10pt]
}
%\author{Your Name}
\date{}

\begin{document}

\maketitle


%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%FILL IN YOUR NAME%%%%%%%
%%%%%%%%%%AND STUDENT ID%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
Due Date \dotfill TODO \\
Name \dotfill \textbf{Didi Trifonova} \\
Student ID \dotfill \textbf{109388776} \\


\tableofcontents

\section{Instructions}
 \begin{itemize}
	\item The solutions \textbf{should be typed}, using proper mathematical notation. We cannot accept hand-written solutions. \href{http://ece.uprm.edu/~caceros/latex/introduction.pdf}{Here's a short intro to \LaTeX.}
	\item You should submit your work through the \textbf{class Canvas page} only. Please submit one PDF file, compiled using this \LaTeX \ template.
	\item You may not need a full page for your solutions; pagebreaks are there to help Gradescope automatically find where each problem is. Even if you do not attempt every problem, please submit this document with no fewer pages than the blank template (or Gradescope has issues with it).

	\item You \textbf{may not collaborate with other students}. \textbf{Copying from any source is an Honor Code violation. Furthermore, all submissions must be in your own words and reflect your understanding of the material.} If there is any confusion about this policy, it is your responsibility to clarify before the due date. 

	\item Posting to \textbf{any} service including, but not limited to Chegg, Discord, Reddit, StackExchange, etc., for help on an assignment is a violation of the Honor Code.

	\item You \textbf{must} virtually sign the Honor Code (see Section \ref{HonorCode}). Failure to do so will result in your assignment not being graded.
\end{itemize}


\section{Honor Code (Make Sure to Virtually Sign)} \label{HonorCode}

\begin{required}
\noindent 
\begin{itemize}
\item My submission is in my own words and reflects my understanding of the material.
\item I have not collaborated with any other person.
\item I have not posted to external services including, but not limited to Chegg, Discord, Reddit, StackExchange, etc.
\item I have neither copied nor provided others solutions they can copy.
\end{itemize}

%\noindent In the specified region below, clearly indicate that you have upheld the Honor Code. Then type your name. 
\end{required}

\begin{proof}[Agreed (Didi Trifonova).]
\end{proof}



\newpage
\section{Standard 5- Exchange Arguments}
\subsection{Problem \ref{DFS1}}
\begin{required} \label{DFS1}
Consider the interval scheduling problem from class. You are given a set of intervals $\mathcal{I}$, where each interval has a start and finish time $[s_i, f_i]$. Your goal is to select a subset $S$ of the given intervals such that (i) no two intervals in $S$ overlap, and (ii) $S$ contains as many intervals as possible subject to condition (i). 

Suppose we have two intervals with the same start time but different finish times. That is, let $I_{1} = [s, f_{1}]$ and $I_{2} = [s, f_{2}]$ with $f_{2} > f_{1}$. 
\begin{enumerate}[label=(\alph*)]
\item Let $\text{overlap}([s, f])$ denote the number of intervals of $\mathcal{I}$ (excluding $[s, f]$) with which $[s, f]$ overlaps. Explain carefully why $\text{overlap}(I_{1}) \leq \text{overlap}(I_{2})$.
\begin{proof}[Answer] $ $\\
For this problem, all of $I_1$ is contained in $I_2$ because they have the same start time and $I_2$ ends after $I_1$. Therefore, anything that overlaps $I_1$ must also overlap $I_2$ in which case $\text{overlap}(I_{1}) = \text{overlap}(I_{2})$. However, there may also be intervals the begin after $f_1 $ and before $f_2$ in which case $\text{overlap}(I_{1}) > \text{overlap}(I_{2})$. Therefore, $\text{overlap}(I_{1}) \leq \text{overlap}(I_{2})$.
\end{proof}


\vskip 50pt
\item Suppose that $\text{overlap}(I_{1}) < \text{overlap}(I_{2})$. Explain carefully why $I_{2}$ can safely be exchanged for $I_{1}$ (that is, in any non-overlapping set of intervals containing $I_1$, replacing $I_1$ by $I_2$ always results in another non-overlapping set of intervals, no smaller than the one we started with). 
\begin{proof}[Answer] $  $ \\
Say you 3 have intervals, $I_1,I_2$ and $I_3$ \\
If $\text{overlap}(I_{1}) < \text{overlap}(I_{2})$ then $I_3$ overlaps with $I_2$ but not with $I_1$.
\begin{enumerate}
    \item Begin with the set of non-overlapping intervals containing $I_2$. $\mathcal{I} = \{I_2\}$. 
    \item $I_1$ and $I_3$ cannot be added because they overlap $I_2$. 
    \item Replace $I_2$ with $I_1$ so that $\mathcal{I}_1 = \{I_1\}$
    \item Now that $I_2$ has been removed, $I_3$ can be added because $I_1$ does not overlap it.  
    \item $\mathcal{I}_1 = \{I_1,I_3\}$
    \item $|\mathcal{I}_1| > |\mathcal{I}| $
\end{enumerate}
This will work for any amount of intervals because removing the interval with more overlaps means we can add additional intervals that previously overlapped. 
\end{proof}
\end{enumerate}
\end{required}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document} % NOTHING AFTER THIS LINE IS PART OF THE DOCUMENT



